---
title: "Datasets for POS 5737"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This package contains only datasets--the tidy datasets for POS 5737 found on the [data page](https://pos5737.github.io/data.html) of the course website.

## Quick 

## Motivation

In the usual workflow, one might download the data file `parties.rds` into the `data/` directory. They might load the data with

```
parties_df <- readr::read_rds("data/parties.rds)
```

This package allows you to skip the download step.

## Usage

### Installing the Package

To install the package, run 

```
devtools::install_github("pos5737/pos5737data")
```

You only need to run this once.

### Loading the Data

Once you have the package installed on your computer, you can load the datasets with

```{r}
# load data
data(parties_df, package = "pos5737data")
```

Alternatively, you can use

```{r}
# load packages
library(pos5737data)

# load data
data("parties_df")
```

To see the available datasets, use

```
help(package = "pos5737data")
```

## Example

```{r message=FALSE, warning=FALSE}
# load packages
library(tidyverse)
library(broom)

# load data
data(parties_df, package = "pos5737data")

# regression model from their table 2, pooled analysis, whole sample
fit <- lm(enep ~ log(average_magnitude)*eneg + upper_tier*eneg + 
            en_pres*proximity, 
          data = parties_df)

# create table
texreg::screenreg(fit)
```






